The impact of early massive mergers on the chemical evolution of Milky Way-like galaxies: insights from NIHAO-UHD simulations

### 2023-05-12 src/tex/ms.tex
fix path to static figure
fixing path for static figure once again
[showyourwork] overleaf sync

\author[T. Buck] {Tobias Buck$^{1,2}$\thanks{E-mail: tobias.buck@iwr-uni-heidelberg.de.de}, Aura Obreja$^{3}$, Bridget Ratcliffe$^{4}$, Yuxi(Lucy) Lu$^{5, 6}$, 
\newauthor Ivan Minchev$^{4}$, Andrea V. Macci\`o$^{7,8}$ \\  %, \etal \\
%, Aaron A. Dutton$^{2}$, Andrea V. Macci\`o$^{2,1}$\\
%
$^1$Universit\"at Heidelberg, Interdisziplin\"ares Zentrum f\"ur Wissenschaftliches Rechnen, Im Neuenheimer Feld 205, \\ D-69120 Heidelberg, Germany\\
$^2$Universit\"at Heidelberg, Zentrum f\"ur Astronomie, Institut f\"ur Theoretische Astrophysik, Albert-Ueberle-Straße 2, \\ D-69120 Heidelberg, Germany\\
$^3$Universit\"ats-Sternwarte M\"unchen, Scheinerstraße 1, D-81679 M\"unchen, Germany\\
${4}$Leibniz Institute for Astrophysics Potsdam, An der Sternwarte 16, 14482 Potsdam, Germany\\
$^{5}$Department of Astronomy, Columbia University, 550 West 120$^{\rm th}$ Street, New York, NY, USA\\
$^{6}$American Museum of Natural History, Central Park West, Manhattan, NY, USA\\
$^7$New York University Abu Dhabi, PO Box 129188, Saadiyat Island, Abu Dhabi, United Arab Emirates\\
$^8$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany
}

@@

\textbf{We have visualized this quantitative finding from Fig.~\ref{fig:feh_evolution} by plotting the cold gas surface density during the time of the gas rich merger for galaxy g2.79e12 in Fig.~\ref{fig:visu} and Fig.~\ref{fig:visu}. Here we show in the left column the total cold gas surface density and split it into the enriched ($\mathrm{[Fe/H]}>-1$) and an unenriched ($\mathrm{[Fe/H]}<-1$) contribution in the middle and right columns where our separating metallicity of $\mathrm{[Fe/H]}=-1$ is motivated by the shape of the MDF in Fig.~\ref{fig:mdf}. This figure clearly reveals how the merging satellite brings in a huge portion of unenriched cold gas that mainly settles into the outskirts of the pre-existing gas disk as we have seen from Fig.~\ref{fig:feh_evolution}. In total, the elevated, unenriched gas surface in the galaxy's outskirt survives for about 2.5-3 Gyr until its gas is consumed or heated up.}

>>>>

\author[T. Buck] {Tobias Buck$^{1,2}$\thanks{E-mail: tobias.buck@iwr-uni-heidelberg.de.de}, Aura Obreja$^{3}$, Bridget Ratcliffe$^{4}$, Yuxi(Lucy) Lu$^{5, 6}$, 
\newauthor Ivan Minchev$^{4}$, Andrea V. Macci\`o$^{7,8,9}$ \\  %, \etal \\
%, Aaron A. Dutton$^{2}$, Andrea V. Macci\`o$^{2,1}$\\
%
$^1$Universit\"at Heidelberg, Interdisziplin\"ares Zentrum f\"ur Wissenschaftliches Rechnen, Im Neuenheimer Feld 205, \\ D-69120 Heidelberg, Germany\\
$^2$Universit\"at Heidelberg, Zentrum f\"ur Astronomie, Institut f\"ur Theoretische Astrophysik, Albert-Ueberle-Straße 2, \\ D-69120 Heidelberg, Germany\\
$^3$Universit\"ats-Sternwarte M\"unchen, Scheinerstraße 1, D-81679 M\"unchen, Germany\\
${4}$Leibniz Institute for Astrophysics Potsdam, An der Sternwarte 16, 14482 Potsdam, Germany\\
$^{5}$Department of Astronomy, Columbia University, 550 West 120$^{\rm th}$ Street, New York, NY, USA\\
$^{6}$American Museum of Natural History, Central Park West, Manhattan, NY, USA\\
$^7$New York University Abu Dhabi, PO Box 129188, Saadiyat Island, Abu Dhabi, United Arab Emirates\\
$^8$Center for Astro, Particle and Planetary Physics (CAP3), New York University Abu Dhabi\\
$^9$Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, 69117 Heidelberg, Germany
}

@@

\textbf{We have visualized this quantitative finding from Fig.~\ref{fig:feh_evolution} by plotting the cold gas surface density during the time of the gas rich merger for galaxy g2.79e12 in Fig.~\ref{fig:visu} and Fig.~\ref{fig:visu}. The panels in Fig.~\ref{fig:visu} and Fig.~\ref{fig:visu} are chosen such that they bracket the times before the merger (i.e. $t=1.99$ Gyr), during the merger event and final coalescence ($t=2.32, 2.84, 3.27$ Gyrs; Fig.~\ref{fig:visu}) as well as for some time after it to show the decrease in cold gas surface density by gas consumption and feedback ($t=3.76, 3.97, 4.54, 5.10$ Gyrs, Fig.~\ref{fig:visu2}). In these figures we show in the left column the total cold gas surface density and split it into the enriched ($\mathrm{[Fe/H]}>-1$) and an unenriched ($\mathrm{[Fe/H]}<-1$) contribution in the middle and right columns where our separating metallicity of $\mathrm{[Fe/H]}=-1$ is motivated by the shape of the MDF in Fig.~\ref{fig:mdf}. This figure clearly reveals how the merging satellite brings in a huge portion of unenriched cold gas that mainly settles into the outskirts of the pre-existing gas disk as we have seen from Fig.~\ref{fig:feh_evolution}. In total, the elevated, unenriched gas surface in the galaxy's outskirt survives for about 2.5-3 Gyr until its gas is consumed or heated up.}
